### 2022-06-07 src/text/2-package-subsections/maps.tex
ref not cite

The sub-package provides a uniform API for the FITS World Coordinate System
(WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and
region-based data structure (see Figure~\cite{ig*:minted:gp_maps}).

>>>>

The sub-package provides a uniform API for the FITS World Coordinate System
(WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and
region-based data structure (see Figure~\ref{ig*:minted:gp_maps}).
